\documentclass[10pt, letterpaper]{article}

\usepackage[
    top=1.45cm,
    bottom=1.35cm,
    left=1.65cm,
    right=1.65cm,
    footskip=0.70cm
]{geometry}
\usepackage{array}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{iftex}
\usepackage{lastpage}
\usepackage{microtype}
\usepackage{tabularx}
\usepackage[dvipsnames]{xcolor}
\usepackage[
    pdftitle={Xinhai Chang's CV},
    pdfauthor={Xinhai Chang},
    pdfcreator={LaTeX},
    hidelinks
]{hyperref}
\usepackage{bookmark}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\small\color{gray!65}\thepage\ of \pageref*{LastPage}}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\emergencystretch=2em
\hyphenpenalty=10000
\exhyphenpenalty=10000
\raggedright
\urlstyle{same}

\definecolor{ink}{HTML}{111111}
\definecolor{visionColor}{HTML}{FF8B94}
\definecolor{robotColor}{HTML}{6EB5FF}
\definecolor{dividerColor}{HTML}{AEB7C2}
\definecolor{mutedText}{HTML}{777777}
\color{ink}

\newcommand{\cvtag}{\textcolor{visionColor}{\raisebox{1pt}{\scalebox{0.58}{\faCircle}}}}
\newcommand{\robtag}{\textcolor{robotColor}{\raisebox{1pt}{\scalebox{0.58}{\faCircle}}}}
\newcommand{\bothTags}{\cvtag\hspace{2.6pt}\robtag}
\newcommand{\corrtag}{\textdagger}
\newcommand{\corrmark}{\nobreak\hspace{0.5pt}\textsuperscript{\corrtag}}
\newcommand{\legend}{\small * equal contribution \quad \corrtag\ corresponding author \quad \cvtag\ computer vision \quad \robtag\ robotics\normalsize\par\vspace{0.18cm}}
\newcommand{\headersep}{\kern 5pt\textcolor{gray!50}{|}\kern 5pt}
\newcommand{\headicon}[1]{\textcolor{mutedText}{\faIcon{#1}}\hspace{0.28em}}

\newlength{\cvlabelwidth}
\setlength{\cvlabelwidth}{2.85cm}
\newlength{\cvsectiongap}
\setlength{\cvsectiongap}{0.35cm}
\newlength{\cvcontentoffset}
\setlength{\cvcontentoffset}{3.20cm}

\newlist{cvblocks}{description}{1}
\setlist[cvblocks]{
    leftmargin=\cvcontentoffset,
    labelwidth=\cvlabelwidth,
    labelsep=\cvsectiongap,
    align=parleft,
    font=\normalfont\small\scshape,
    topsep=0pt,
    partopsep=0pt,
    itemsep=0pt,
    parsep=0pt
}

\newif\ifcvfirstsection
\cvfirstsectiontrue
\newif\ifshowsectiondividers
\showsectiondividerstrue % Use \showsectiondividersfalse to hide lines while preserving spacing.
\newcommand{\resetsectiondivider}{\global\cvfirstsectiontrue}
\newcommand{\cvdivider}{%
    \par\vspace{0.17cm}%
    \noindent\hspace*{\cvcontentoffset}%
    \makebox[\dimexpr\linewidth-\cvcontentoffset\relax][l]{%
        \ifshowsectiondividers
            {\color{dividerColor}\xleaders\hbox{\rule{4pt}{0.35pt}\hspace{3pt}}\hfill\kern0pt}%
        \else
            \rule{0pt}{0.35pt}%
        \fi
    }%
    \par\vspace{0.15cm}%
}
\newcommand{\cvsection}[2]{%
    \ifcvfirstsection
        \global\cvfirstsectionfalse
        \vspace{0.24cm}
    \else
        \cvdivider
    \fi
    \begin{cvblocks}
        \item[#1] #2
    \end{cvblocks}
}
\newcommand{\justifiedparagraph}[1]{%
    \begingroup
    \rightskip=0pt plus 0pt
    \leftskip=0pt
    \parfillskip=0pt plus 1fil
    \spaceskip=0pt
    \xspaceskip=0pt
    #1\par
    \endgroup
}

\newcommand{\datedline}[2]{%
    \noindent
    \begin{tabularx}{\linewidth}{@{}X@{\hspace{0.45cm}}r@{}}
        #1 & #2
    \end{tabularx}\par
}
\newcommand{\edudetail}[1]{%
    \noindent\hspace*{1.05em}#1\par
}

\newcommand{\pubitem}[3]{%
    \noindent
    \begin{tabularx}{\linewidth}{@{}r@{\hspace{0.55em}}X@{}}
        [#1] & #2\nobreak\hspace{0.25em}\mbox{#3}
    \end{tabularx}\vspace{0.15cm}
}

\newcommand{\recordgap}{\vspace{0.13cm}}
\newcommand{\entrygap}{\vspace{0.18cm}}

\newenvironment{compactitems}{%
    \begin{itemize}[leftmargin=1.15em, topsep=0.04cm, itemsep=0pt, parsep=0pt, partopsep=0pt]
}{%
    \end{itemize}
}

\begin{document}

\begin{center}
    {\fontsize{21pt}{23pt}\selectfont\scshape Xinhai Chang}\par
    \vspace{0.21cm}
    {\small
    \headicon{globe}\href{https://chang-xinhai.github.io/}{chang-xinhai.github.io} \headersep
    \headicon{map-marker-alt}Beijing, China \headersep
    \headicon{envelope}\href{mailto:walkerch0466@gmail.com}{walkerch0466@gmail.com}\par
    \vspace{0.075cm}
    \textcolor{mutedText}{\faGithub}\hspace{0.28em}\href{https://github.com/chang-xinhai}{chang-xinhai} \headersep
    \headicon{graduation-cap}\href{https://scholar.google.com/citations?user=NVxBzq4AAAAJ}{Google Scholar} \headersep
    {\color{mutedText}\headicon{calendar-alt}Updated: July 13, 2026}
    }
\end{center}

\vspace{-0.04cm}

\cvsection{Research\\Interests}{
    \justifiedparagraph{I work at the intersection of \textbf{3D vision}, \textbf{robot learning}, and \textbf{embodied AI}. I focus on \textbf{Real-Sim-Real} systems that connect real-world perception, simulation, and robotic manipulation. My broader interests include 3D reconstruction and generation, world models, visuomotor policy learning, scalable simulation, and generalizable robot manipulation.}
}

\cvsection{Education}{
    \datedline{\textbf{Bachelor of Science in Data Science}, Peking University}{Expected June 2027}
    \edudetail{Yuanpei College, Beijing, China}
    \edudetail{\textbf{GPA:} 3.76/4.0}
    \edudetail{\textbf{Coursework:} Computer Vision, Multimodal Learning, Intelligent Robotics [3.9+]}
}

\cvsection{Research\\Experience}{
    \datedline{\textbf{Research Assistant}, VCL Lab, Peking University}{June 2026 -- Present}
    \textit{Advised by Prof. Wenzheng Chen}
    \begin{compactitems}
        \item Research on robot learning and world models for embodied AI, with an emphasis on depth perception, navigation, and real-world robotic manipulation.
    \end{compactitems}

    \entrygap
    \datedline{\textbf{Research Assistant}, CoRe Lab, Peking University}{March 2025 -- June 2026}
    \textit{Advised by Prof. Yixin Zhu}
    \begin{compactitems}
        \item Research on scalable simulation and planning for mobile and dexterous manipulation, including trajectory generation, tactile-guided control, and policy evaluation.
    \end{compactitems}

    \entrygap
    \datedline{\textbf{Research Assistant}, Media Lab and EECS, MIT}{March 2024 -- Present}
    \textit{Mentored by Kaichen Zhou}
    \begin{compactitems}
        \item Research on 3D/4D perception and generative world models, including 3D reconstruction, 3D editing, 3D generation, world action models, and multi-view benchmarks.
    \end{compactitems}
}

\cvsection{Technical\\Skills}{
    \textbf{Robotics:} Robot manipulation, mobile manipulation, dexterous manipulation, trajectory planning, large-scale simulation, visuomotor policy learning and evaluation; Isaac Lab, Isaac Sim, cuRobo.\par
    \textbf{3D Vision:} 3D reconstruction, 3D editing, 3D generation, 4D perception, world models, SLAM, depth estimation, multimodal learning.\par
    \textbf{Programming:} Python, C/C++, Bash, HTML, CSS; PyTorch, TensorFlow, Pandas, Qt.
}

\cvsection{Publications}{
    \legend
    \pubitem{7}{Jiaheng Li, Binsheng Zhang, \textbf{Xinhai Chang}, Wenzheng Chen\corrmark. \textit{NSL-SLAM: High-Fidelity Neural Structured-Light Depth for Practical SLAM and Reconstruction}. ACM International Conference on Multimedia (ACM MM), 2026.}{\cvtag}
    \pubitem{6}{Kaichen Zhou*, Yuzhen Chen*, Fangneng Zhan, Hang Hua, Grace Chen, \textbf{Xinhai Chang}, Ao Qu, Yilun Du, Zhuang Liu, Paul Pu Liang\corrmark, Mengyu Wang\corrmark. \href{https://arxiv.org/abs/2605.22882}{\textit{GEM-4D: Geometry-Enhanced Video World Models for Robot Manipulation}}. European Conference on Computer Vision (ECCV), 2026.}{\bothTags}
    \pubitem{5}{Yida Niu*, \textbf{Xinhai Chang}*, Xin Liu*, Ziyuan Jiao\corrmark, Yixin Zhu\corrmark. \href{https://yzhu.io/publication/tamp2026cvpr/paper.pdf}{\textit{Scalable Trajectory Generation for Whole-Body Mobile Manipulation}}. Computer Vision and Pattern Recognition, Highlight, 2026.}{\robtag}
    \pubitem{4}{\textbf{Xinhai Chang}, Kaichen Zhou\corrmark. \href{https://arxiv.org/abs/2406.04301}{\textit{Neural Surface Reconstruction from Sparse Views Using Epipolar Geometry}}. Computer Vision and Pattern Recognition Workshop A2AMML, 2026.}{\cvtag}
    \pubitem{3}{Kaichen Zhou, Yuhan Wang*, Grace Chen*, \textbf{Xinhai Chang}*, Gaspard Beaudouin, Fangneng Zhan, Paul Pu Liang\corrmark, Mengyu Wang\corrmark. \href{https://arxiv.org/abs/2510.17568}{\textit{PAGE-4D: Disentangled Pose and Geometry Estimation for 4D Perception}}. International Conference on Learning Representations (ICLR), 2026.}{\cvtag}
    \pubitem{2}{Hongze Li*, Xuchuan Huang*, \textbf{Xinhai Chang}*, Jun Zhou, Huijing Zhao\corrmark. \href{https://ieeexplore.ieee.org/document/11246334}{\textit{TerraX: Visual Terrain Classification Enhanced by Vision-Language Models}}. International Conference on Intelligent Robots and Systems (IROS), Oral, 2025.}{\bothTags}
    \pubitem{1}{Kaichen Zhou*, Lanqing Hong*, \textbf{Xinhai Chang}*, Yingji Zhong, Enze Xie, Hao Dong, Zhihao Li, Yongxin Yang, Zhenguo Li, Wei Zhang. \href{https://arxiv.org/abs/2312.15856}{\textit{SplatMesh: Interactive 3D Segmentation and Editing Using Mesh-Based Gaussian Splatting}}. CVPR 2025 Workshop.}{\cvtag}
}

\cvsection{Preprints}{
    \legend
    \pubitem{2}{Kaichen Zhou*, \textbf{Xinhai Chang}*, Taewhan Kim*, Jiadong Zhang*, Yang Cao, Chufei Peng, Fangneng Zhan, Hao Zhao, Hao Dong, Kai Ming Ting, Ye Zhu\corrmark. \href{https://arxiv.org/abs/2410.00713v3}{\textit{RAD: A Realistic Multi-View Benchmark for Pose-Agnostic Anomaly Detection}}. Under Review, 2026.}{\bothTags}
    \pubitem{1}{Kaichen Zhou*, Zeyang Bai*, \textbf{Xinhai Chang}*, Mengyu Wang\corrmark, Paul Pu Liang\corrmark, Fangneng Zhan\corrmark. \href{https://arxiv.org/abs/2605.21472}{\textit{Stream3D: Sequential Multi-View 3D Generation via Evidential Memory}}. Under Review, 2026.}{\cvtag}
}

\cvsection{Honors and\\Awards}{
    \datedline{\textbf{National Scholarship} (highest honor for undergraduate students in China)}{2025}
    \recordgap
    \datedline{Second-class Scholarship, Peking University}{2024}
    \recordgap
    \datedline{First Prize, 21st Jiang Zehan Cup Mathematical Modeling Competition}{2024}
    \recordgap
    \datedline{Xing Zhengde Scholarship, Yuanpei College}{2023}
    \recordgap
    \datedline{Third-class Scholarship, Peking University}{2023}
}

\cvsection{Teaching\\Experience}{
    \datedline{\textbf{Teaching Assistant}, Introduction to Computation B (Prof. Jun Sun)}{Autumn 2025}
    Led weekly programming labs, graded assignments, and designed exam questions.\par
    \entrygap
    \datedline{\textbf{Teaching Assistant}, Introduction to Computation C (Prof. Baobao Chang)}{Autumn 2025}
    Led weekly programming labs, graded assignments, and designed exams and the final project.\par
    \entrygap
    \datedline{\textbf{Teaching Assistant}, Introduction to Computer Systems (Prof. Lu Zhang)}{Autumn 2024}
    Led weekly discussion sessions, graded assignments, and contributed to exam design.
}

\cvsection{Service and\\Outreach}{
    \datedline{Volunteer Teacher, Student Development Center, Peking University}{Spring 2026}
    \recordgap
    \datedline{Volunteer Teacher, Student Development Center, Peking University}{Autumn 2025}
    \recordgap
    \datedline{Volunteer Teacher, International Asian Liver Center, Gansu, China}{Summer 2024}
    \recordgap
    \datedline{Volunteer, Yunnan Golden Monkey Conservation, Peking University}{Winter 2023}
}

\end{document}
